---
title: "Developing Data Products Week 2 Assignment"
author: "Daisy Wu"
date: "2018年3月28日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions
Create a web page using R Markdown that features a map created with leaflet

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the data that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## Review criteria
The rubric contains the following two questions:
 1. Does the web page feature a date and is this date less than two months before the date that you're garding this assignment?
 2. Does the Web page feature an interactive map that appears to have been created with Leaflet?
 

## Submission

Here is the Danei Market, Totoro bus stop, Danei District, CPC and 7-Eleven store 
Some of the visiting location in Dainei, Tainan of Taiwan

```{r}
library(knitr)
library(leaflet)
library(dplyr)
```

```{r}
m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lat=23.118851, lng=120.358230, popup="Danei Market") %>%
  addMarkers(lat=23.124255,lng=120.356067, popup="Totoro bus stop") %>%
  addMarkers(lat=23.118995,lng=120.360268, popup="Danei District") %>%
  addMarkers(lat=23.121305,lng=120.354849, popup="CPC") %>%
  addMarkers(lat=23.119312,lng=120.356262, popup="7-Eleven") #%>%
  
  
m  # Print the map
```

# Mapping Clusters
When you zoom in to each cluster, the cluster will seperate until you see the individual Markers

```{r}
df <- data.frame(lat=runif(500, min=23.10, max=23.13),
                 lng=runif(500, min=120.35, max=120.37))
```

```{r}
df %>%
leaflet() %>%
addTiles() %>%  
addMarkers(clusterOptions = markerClusterOptions())  
```

